What is a partial correlation?

### 2024-12-14 text/23/what-is-a-partial-correlation.Rmd

```{r partial-correlation-01, echo=FALSE, warning=FALSE, message=FALSE}
library(broom)
library(tidyverse)
fn <- "https://raw.githubusercontent.com/pmean/classes/master/biostats-1/data/data-05-fev.csv"
read_csv(
    fn, 
    col_names=FALSE, 
    col_types="n") %>%
    data.frame -> init
names(init) <- c(
  "age",
  "fev",
  "height",
  "sex",
  "smoker")
```

>>>>

```{r partial-correlation-01, echo=FALSE, warning=FALSE, message=FALSE}
library(broom)
library(tidyverse)
fn <- "https://raw.githubusercontent.com/pmean/data/refs/heads/main/files/fev.csv"
read_csv(
    fn, 
    col_names=FALSE, 
    col_types="n") %>%
    data.frame -> init
names(init) <- c(
  "age",
  "fev",
  "height",
  "sex",
  "smoker")
```
